Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-06-04 WSSSPE1_report/WSSSPE1_summary_report.tex
style error corrected

One such example is the \toolname{Galaxy} project~\cite{Galaxy}. It follows
agile software development practices and implements standards such as
test-driven development and socialized bug managing practices via
\toolname{trello}. \toolname{Galaxy} \emph{histories} and \emph{toolshed} offer
easy community sharing of data and tools further promoting a collaborative
environment. The project closely follows the guidelines described in Carver and
Thiruvathukal~\cite{Carver_WSSSPE} and many from Prli\'{c} and
Procter~\cite{Prlic_WSSSPE}. Many utility software projects are often developed
aiming better utilizing a particular, new infrastructure and architecture,
e.g., \toolname{MVAPICH} (original release 2002), \toolname{VisIT}, \toolname{ParaView}. Similarly, to
leverage the power of emerging architectures such as accelerators, new code and
libraries are required. The experience of one such effort as described in
Ferenbaugh~\cite{Ferenbaugh_WSSSPE} which met with a limited success but
nonetheless with many invaluable lessons were learned about influential
cultural and technical aspects in sustainable software development practices.

>>>>

One such example is the \toolname{Galaxy} project~\cite{Galaxy}. It follows
agile software development practices and implements standards such as
test-driven development and socialized bug managing practices via
\toolname{trello}. \toolname{Galaxy} \emph{histories} and \emph{toolshed} offer
easy community sharing of data and tools further promoting a collaborative
environment. The project closely follows the guidelines described in Carver and
Thiruvathukal~\cite{Carver_WSSSPE} and many from Prli\'{c} and
Procter~\cite{Prlic_WSSSPE}. Many utility software projects are often developed
aiming better utilizing a particular, new infrastructure and architecture,
e.g., \toolname{MVAPICH} (o.r. 2002), \toolname{VisIT}, \toolname{ParaView}. Similarly, to
leverage the power of emerging architectures such as accelerators, new code and
libraries are required. The experience of one such effort as described in
Ferenbaugh~\cite{Ferenbaugh_WSSSPE} which met with a limited success but
nonetheless with many invaluable lessons were learned about influential
cultural and technical aspects in sustainable software development practices.
